Assessing Digital Elevation Models with different image overlap using photogrammetry

### 2021-04-23 Paper.tex
20200423 backup

\subsection{Study Area}\label{sec:Study Area}
The data covers an area in Ghana, about 20km south east of Ejura (lat. 7.3064212, lon. -1.164493). 
The area of interest is about 25000 m\textsuperscript{2}. 
The area consists mostly of sanvannah.
There are a few trees present.
\begin{figure}[htp]
    \centering
    \includegraphics[width=4cm]{locationwide.png}
    \includegraphics[width=4cm]{imgloc.png}
    \caption{Area of Interest and Unprocessed Image GPS Locations}
    \label{fig:areaofinterest}
\end{figure}
Each image has a resolution of 4000 times 3000 and was taken by a DJI Phantom 3.
The images all contain GNNS location (WGS84). 
The complete data set consists of 111 images.
Their exact location can be found in figure \ref{fig:areaofinterest}.

\subsection{Image Processing}
For image processing and DEM generation Agisoft Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used \citep{AgisoftMetashape}.
First, the complete data set has been aligned on medium quality.
Next, the dense cloud was built on medium quality (no depth filtering), resulting in a dense cloud of 3,268,264 points.
A mesh was built using the the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
After the mesh the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
The mesh was set to create a 2.5D height field.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=4cm]{loc_low.png}
    \includegraphics[width=4cm]{loc_med.png}
    \includegraphics[width=4cm]{loc_full.png}
    \includegraphics[width=4cm]{loc_high.png}
    \caption{Estimated camera location. 
    White: used in the image processing, red: disabled in the image processing.\\
    Clockwise (starting left top): low, medium, high and full settings}
    \label{fig:cameralocation}
\end{figure}

@@

\begin{table}[htb]
    \centering
    \caption{Image Processing Results}
    \begin{tabular}{@{}cccc@{}}
    \toprule
    \textbf{Setting} & \textbf{Images} & \multicolumn{1}{l}{\textbf{Sparse Cloud}} & \multicolumn{1}{l}{\textbf{Dense Cloud}} \\ \midrule
    -      & 111 & 80,901 & 3,269,264 \\
    Low    & 44  & 37,886 & 4,172,783 \\
    Medium & 70  & 54,556 & 3,313,399 \\
    High   & 75  & 49,692 & 3,276,832 \\ \bottomrule
    \label{tab:ImageProcessing}
\end{tabular}
\end{table}

\subsection{DEM}
The source data for the DEM's are the dense cloud results. 
The Dense Cloud contains about the same amount of points with the exception for the lowest Reduce Overlap setting.
This setting has resulted in the dense cloud with the most points.
The TIN algorithm is used to built the DEM's \citep{axelsson1999processing}.
The image overlap is now changed, therefore the DEM's have a slightly different extent.
Because of this the largest common extent of the DEM's will be used to crop the DEM's resulting in four DEM's with an equal extent.
The DEM's will also be scaled to check the differences between the DEM's without looking at the absolute values.
The scaling will be done by subtracting the mean and dividing by the standard deviation.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=8cm]{DemPlots.png}
    \caption{DEM Results of the Reduce Overlap}
    \label{fig:DemPlot_unscaled}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=8cm]{DemBoxplot.png}
    \caption{Box plots of the DEM Results of the Reduce Overlap}
    \label{fig:BoxPlot_unscaled}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=8cm]{DemPlots_scaled.png}
    \caption{Scaled DEM Results of the Reduce Overlap}
    \label{fig:DemPlot_scaled}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=8cm]{DemBoxPlot_Scaled.png}
    \caption{Scaled DEM Results of the Reduce Overlap}
    \label{fig:BoxPlot_scaled}
\end{figure}

>>>>

\subsection{Study Area}\label{sec:Study Area}
The data covers an area in Ghana, about 20km south east of Ejura (lat. 7.3064212, lon. -1.164493). 
The area of interest is about 25000 m\textsuperscript{2}. 
The area consists mostly of sanvannah.
There are a few trees present.
\begin{figure}[h]
    \centering
    \includegraphics[width=4cm]{locationwide.png}
    \includegraphics[width=4cm]{imgloc.png}
    \caption{Area of Interest and Unprocessed Image GPS Locations}
    \label{fig:areaofinterest}
\end{figure}
Each image has a resolution of 4000 times 3000 and was taken by a DJI Phantom 3.
The images all contain GNNS location (WGS84). 
The complete data set consists of 111 images.
Their exact location can be found in figure \ref{fig:areaofinterest}.

\subsection{Image Processing}
For image processing and DEM generation Agisoft Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used \citep{AgisoftMetashape}.
All data have been processed on the cloud service provided by Agisoft (\url{https://cloud.agisoft.com}).
The cloud processing is done on a vCPU (Intel Xeon E5 2686 v4) with two NVIDIA Tesla M60 GPU's and 240 GB of RAM.

First, the complete data set has been aligned on medium quality.
Next, the dense cloud was built on medium quality (no depth filtering), resulting in a dense cloud of 3,268,264 points.
A mesh was built using the the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
After the mesh the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
The mesh was set to create a 2.5D height field.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=4cm]{loc_low.png}
    \includegraphics[width=4cm]{loc_med.png}
    \includegraphics[width=4cm]{loc_full.png}
    \includegraphics[width=4cm]{loc_high.png}
    \caption{Estimated camera location. 
    White: used in the image processing, red: disabled in the image processing.\\
    Clockwise (starting left top): low, medium, high and full settings}
    \label{fig:cameralocation}
\end{figure}

@@

\begin{table}[h]
    \centering
    \caption{Image Processing Results}
    \begin{tabular}{@{}cccc@{}}
    \toprule
    \textbf{Setting} & \textbf{Images} & \multicolumn{1}{l}{\textbf{Sparse Cloud}} & \multicolumn{1}{l}{\textbf{Dense Cloud}} \\ \midrule
    -      & 111 & 80,901 & 3,269,264 \\
    Low    & 44  & 37,886 & 4,172,783 \\
    Medium & 70  & 54,556 & 3,313,399 \\
    High   & 75  & 49,692 & 3,276,832 \\ \bottomrule
    % Add processing time!
    \label{tab:ImageProcessing}
\end{tabular}
\end{table}

For all the different settings the processing time can be found in table \ref{tab:processingTime}

\begin{table}[h]
    \centering
    \caption{Processing time in seconds for the difference steps in the process.}
    \label{tab:processingTime}
    \begin{tabular}{@{}cccc@{}}
    \toprule
    \textbf{Setting} & \textbf{Sparse Cloud} & \multicolumn{1}{l}{\textbf{Dense Cloud}} & \multicolumn{1}{l}{\textbf{DEM}} \\ 
    \midrule
    -      & 150 & 292 & 17 \\
    Low    & 59  & 443 & 16 \\
    Medium & 83  & 147 & 17 \\
    High   & 129 & 159 & 17 \\ \bottomrule
\end{tabular}
\end{table}

\subsection{DEM}
The source data for the DEM's are the dense cloud results. 
The Dense Cloud contains about the same amount of points with the exception for the lowest Reduce Overlap setting.
This setting has resulted in the dense cloud with the most points.
The TIN algorithm is used to built the DEM's \citep{axelsson1999processing}.
The image overlap is now changed, therefore the DEM's have a slightly different extent.
Because of this the largest common extent of the DEM's will be used to crop the DEM's resulting in four DEM's with an equal extent.
The DEM's will be exported from Agisoft Metashape with the same pixel resolution of 17.5 cm per pixel.
The DEM's will also be scaled to check the differences between the DEM's without looking at the absolute values.
The scaling will be done by subtracting the mean and dividing by the standard deviation.
For further comparison all of the DEM's will be subtracted from the full model DEM.
This will result in three new DEM's that contain differences instead of height values.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm]{DemPlots.png}
    \caption{DEM Results of the Reduce Overlap}
    \label{fig:DemPlot_unscaled}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm]{DemBoxplot.png}
    \caption{Box plots of the DEM Results of the Reduce Overlap}
    \label{fig:BoxPlot_unscaled}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm]{DemPlots_scaled.png}
    \caption{Scaled DEM Results of the Reduce Overlap}
    \label{fig:DemPlot_scaled}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm]{DemBoxPlot_Scaled.png}
    \caption{Scaled DEM Results of the Reduce Overlap}
    \label{fig:BoxPlot_scaled}
\end{figure}

In figure \ref{fig:ViolinPlot} a violin plot containing the difference of the DEM between the different Reduce Overlap settings can be found.

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm]{ViolinPlot2.png}
    \caption{Violin plot of the difference between the full DEM and the reduced DEM's}
    \label{fig:ViolinPlot}
\end{figure}

% Substract the DEM from each other
